\begin{center}
\begin{longtable}{p{0.5cm}p{0.5cm}p{15cm}}
\toprule
L & O & sentence \\
\toprule
0 & o & i gave pete the book to impress. \\
1 &   & i gave pete the book to impress him. \\
1 & o & most of the fruit is rotten. \\
1 &   & most of the fruit is ripened. \\
1 &   & most of the fruit is spoiled. \\
1 & o & the administration has issued a statement that it is willing to meet a student group, but i'm not sure which one. \\
1 &   & the administration has issued a statement that it is willing to meet a student group. \\
1 & o & the correspondence school sent bill a good typist. \\
1 &   & the school sent bill a good typist. \\
1 &   & the correspondence school sent bill a good baker. \\
1 & o & the report that crime was declining surprised many people. \\
1 &   & the report that crime was declining surprised many. \\
1 &   & the report surprised many people. \\
0 & o & the storm arrived while the picnic. \\
0 &   & the storm arrived while the performance. \\
0 &   & the storm arrived while the picnic was. \\
1 &   & the storm arrived while the picnic was starting. \\
1 &   & the storm arrived during the picnic. \\
1 & o & they chased the man with the car. \\
1 &   & they chased the man with a car. \\
1 & o & they were going to meet sometime on sunday, but the faculty didn't know when. \\
1 &   & they were going to meet sometime on sunday, but the faculty didn't know. \\
1 &   & they were going to meet sometime on sunday. \\
0 & o & we talked to them about there. \\
1 &   & we talked to them about it. \\
1 & o & bill's wine from france and ted's from california cannot be compared. \\
1 &   & bill's wine from france and ted's wine from california cannot be compared. \\
1 &   & bill's wine from france and ted's wine cannot be compared. \\
1 &   & bill's wine and ted's wine cannot be compared. \\
0 & o & brian threw the fence with the stick. \\
1 &   & brian hit the fence with the stick. \\
1 &   & brian attacked the fence with the stick. \\
1 &   & brian poked the fence with the stick. \\
1 &   & brian struck the fence with the stick. \\
0 & o & chris was handed sandy a note. \\
1 &   & chris handed sandy a note. \\
1 &   & chris was handed a note. \\
0 & o & dana walking and leslie ran. \\
1 &   & dana walked and leslie ran. \\
0 & o & john was struck as sick. \\
1 &   & john was treated as sick. \\
1 &   & john was seen as sick. \\
0 & o & john whispered mary left. \\
1 &   & john whispered that mary left. \\
1 &   & john thought mary left. \\
1 &   & john knew mary left. \\
0 & o & leslie told us about us. \\
1 &   & leslie told us about them. \\
1 &   & leslie told them about us. \\
0 & o & my heart is pounding me. \\
1 &   & my heart is pounding. \\
0 &   & my heart is beating me. \\
1 &   & my heart is beating. \\
0 & o & the children are fond that they have ice cream. \\
0 &   & the children are eager that they have ice cream. \\
1 &   & the children are fond of having ice cream. \\
1 &   & the children are glad that they have ice cream. \\
1 &   & the children are happy that they have ice cream. \\
0 & o & the magazines were sent to herself by mary. \\
1 &   & the magazines were sent by mary to herself. \\
1 &   & the magazines were sent to her by mary. \\
0 & o & the table was wiped by john clean. \\
1 &   & the table was wiped clean by john. \\
1 &   & the table was wiped by john. \\
0 & o & we believed john to be a fountain in the park. \\
1 &   & we believed there to be a fountain in the park. \\
0 &   & we believed john to be a fountain. \\
0 &   & we believed john to be a bench in the park. \\
0 &   & we believed john to be a tree in the park. \\
1 &   & we believed john to be a musician in the park. \\
\bottomrule
\caption{Selected CoLA evaluation-set sentences classified correctly by the teacher model but incorrectly by one or both students. L = label (0 = unacceptable, 1 = acceptable), O = original sentence or a manually perturbed (and labelled) variant.}
\label{tab:own-CoLA-diagnostics}
\end{longtable}
\end{center}